---
title: "2019 Education data Summary"
author: "BGD GIS DATA UNIT"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: true
---


```{r setup, include=FALSE, warning = FALSE, message=FALSE}

knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE,
                      warning = FALSE)

source("scripts/match_id_name.R")
write.csv(matched_df_full,"outputs/match_df.csv")


```


## Basic information
Number of observations in 2019-  **`r nrow(dataset_2019_cleaned)`**<br> 
Number of observations in 2018-  **`r nrow(dataset_2018_cleaned)`**<br> 

Number of facilities in 2018- **`r length(dataset_2018_cleaned$centerid %>% unique)`**<br> 
Number of facilities in 2019- **`r length(dataset_2019_cleaned$Facility.ID %>% unique)`**<br> 

Average number of student per facility for 2019 - **`r avr_number_of_student_2019`**<br>
Average number of student per facility for 2018 - **`r avr_number_of_student_2018`**<br>

Unique Progress IDs in 2019- **`r dataset_2019_cleaned$Student.progress.ID %>% unique() %>% length()`** (`r round(dataset_2019_cleaned$Student.progress.ID %>% unique() %>% length()/dataset_2019_cleaned %>% nrow()*100,2)`%) <br> 

<i>***Data Matched by facility IDs***<br>
2019s facility IDs matched with 2018 - **`r faicility_id_2019_in_2018_count`** (`r faicility_id_2019_in_2018_percent`) <br> 
2018s facility IDs matched with 2019 - **`r faicility_id_2018_in_2019_count`** (`r faicility_id_2018_in_2019_percent`) <br> 

<i>**Data Matched by name and facility IDs**</i><br>
 <u>2019s data matched with 2018 - </u> <br> 
                 1. Taking only matched facility IDs -**`r data_2019_in_2018_count`** (`r data_2019_in_2018_percent`)<br> 
                <li>Overall - **`r data_2019_in_2018_count_overall`** (`r data_2019_in_2018_percent_overall`) </li><br> 
                
 <u>2018s data matched with 2019 -  </u><br>
                 1. Taking only matched facility IDs -**`r data_2018_in_2019_count`** (`r data_2018_in_2019_percent`)<br> 
                <li>Overall - **`r data_2018_in_2019_count_overall`** (`r data_2018_in_2019_percent_overall`)</li><br>

## Student per camp
```{r fig.height=50, fig.width=60}


summary_by_camp_2019 <- dataset_2019_cleaned$Camp %>% AMR::freq() %>% as.data.frame() %>% dplyr::mutate(
  year= 2019
)
summary_by_camp_2018 <- dataset_2018_cleaned$Camp %>% AMR::freq() %>% as.data.frame()  %>% dplyr::mutate(
  year= 2018
)

summary_by_camp <- bind_rows(summary_by_camp_2019,summary_by_camp_2018)
summary_by_camp$year <- summary_by_camp$year %>% as.factor()

ggplot(summary_by_camp) +
  geom_bar(aes(x = reorder(item, -count),
               y= count,
               color = year, 
               fill = year),
               position = "dodge",
               stat = "identity")+
  # geom_text(aes(x=item,y=count,label=count),
  #            position = position_dodge(width = .5),size=15)+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(size = 50),
        axis.line = element_blank(),
        axis.text = element_text(size = 50),
        panel.border = element_rect(colour = "black", fill=NA, size=.8),
        panel.background = element_blank(),
        panel.grid.major.x= element_line(size = 1, linetype = "dashed",
                                         colour = "#c1c1c1"),
        # panel.grid.minor.x= element_line(size = 0.5, linetype = "dashed",
        # colour = "#c1c1c1"),
        
        panel.grid.major.y = element_line(size = 1, linetype = "dashed",
                                          colour = "#c1c1c1"),
        # panel.grid.minor.y = element_line(size = 0.5, linetype = "dashed",
        #                                   colour = "#c1c1c1"),
        panel.spacing = unit(0,"cm"),
        legend.title=element_blank(),
        legend.text = element_text(size=50),
        legend.position = "top",
        legend.justification = .45,
        legend.key.width =  unit(1,"cm"),
        legend.spacing.x = unit(.5, "cm"),
        legend.spacing.y = unit(.9, "cm"),
        legend.key.size = unit(1, 'lines'),
        legend.key = element_rect(fill = NA),
        plot.margin = unit(c(.1, .1, 0, 0), "cm"),
        legend.text.align = 0,
        strip.text = element_text(size=50))+
     # scale_colour_continuous(values=c("red", "blue"))+
  ylab("Camp") +
  xlab("Count") +
  coord_flip()

# summary_by_camp %>% kable(longtable = T, booktabs = T, linesep = "",caption= "Number of data per camp") %>% kable_styling(position = "center")
```

## Percentage
  
```{r fig.height=50, fig.width=60}

summary_by_camp_with_unhcr_pop <- summary_by_camp %>% left_join(population_2019,by =c("item"="Camp")) %>% dplyr::mutate(
  percentage_of_total = count/age_1_to_17_total
)

ggplot(summary_by_camp_with_unhcr_pop) +
  geom_bar(aes(x = reorder(item, -percentage_of_total),
               y= percentage_of_total,
               color = year, 
               fill = year),
               position = "dodge",
               stat = "identity")+
  # geom_text(aes(x=item,y=percentage_of_total,label=round(percentage_of_total*100,2)), position=position_dodge(width=0.3), hjust=-.25,size=15)+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(size = 50),
        axis.line = element_blank(),
        axis.text = element_text(size = 50),
        panel.border = element_rect(colour = "black", fill=NA, size=.8),
        panel.background = element_blank(),
        panel.grid.major.x= element_line(size = 1, linetype = "dashed",
                                         colour = "#c1c1c1"),
        # panel.grid.minor.x= element_line(size = 0.5, linetype = "dashed",
        # colour = "#c1c1c1"),
        
        panel.grid.major.y = element_line(size = 1, linetype = "dashed",
                                          colour = "#c1c1c1"),
        # panel.grid.minor.y = element_line(size = 0.5, linetype = "dashed",
        #                                   colour = "#c1c1c1"),
        panel.spacing = unit(0,"cm"),
        legend.title=element_blank(),
        legend.text = element_text(size=50),
        legend.position = "top",
        legend.justification = .45,
        legend.key.width =  unit(1,"cm"),
        legend.spacing.x = unit(.5, "cm"),
        legend.spacing.y = unit(.9, "cm"),
        legend.key.size = unit(1, 'lines'),
        legend.key = element_rect(fill = NA),
        plot.margin = unit(c(.1, .1, 0, 0), "cm"),
        legend.text.align = 0,
        strip.text = element_text(size=50))+
  scale_y_continuous(labels = scales::percent)+
  ylab("Camp") +
  xlab("Percentage") +
  coord_flip()

# summary_by_camp %>% kable(longtable = T, booktabs = T, linesep = "",caption= "Number of data per camp") %>% kable_styling(position = "center")
```

## Number of different level student by camp 
Number of NAs in level column - **`r sum(is.na(df_2019$Level.of.the.student))`** <p>
Number of ECD in level column - **`r sum(df_2019$Level.of.the.student == "ECD",na.rm=T)`** 

```{r fig.height=60, fig.width=60}
# dataset_2019_cleaned$Level.of.the.student <- dataset_2019_cleaned$Level.of.the.student %>% as.factor()


Total_number_of_student_by_level <- dataset_2019_cleaned$Level.of.the.student %>% AMR::freq()
  
Total_number_of_student_by_level %>% kable(longtable = T, booktabs = T, linesep = "",caption= "Number of differnt level student per camp") %>% kable_styling(position = "center")

dataset_2019_cleaned_for_charts <- dataset_2019_cleaned  %>% dplyr::select(Camp,Level.of.the.student) %>%
  dplyr::group_by(Camp,Level.of.the.student) %>% dplyr::summarise(
    count_by_camp_level=n()
  )  %>% ungroup() %>% dplyr::group_by(Camp) %>% dplyr::mutate(
    percentage = count_by_camp_level/sum(count_by_camp_level)
  ) %>% ungroup() %>% dplyr::mutate(
    sum_value = if_else(Level.of.the.student== "level1",count_by_camp_level*1,
                        if_else(Level.of.the.student== "level2",count_by_camp_level*2,
                                if_else(Level.of.the.student== "level3",count_by_camp_level*3,
                                        if_else(Level.of.the.student== "level4",count_by_camp_level*4,99999999999))))
  ) %>% dplyr::group_by(Camp) %>% dplyr::mutate(
    mean_by_camp = sum(sum_value)/sum(count_by_camp_level)
  )

ggplot(dataset_2019_cleaned_for_charts) +
  geom_bar(aes(x = Level.of.the.student,
               y= percentage,
               color = Level.of.the.student, 
               fill = Level.of.the.student),
               position = "dodge",
               stat = "identity")+
  # geom_text(aes(x=Level.of.the.student,y=percentage,label=percentage), position=position_dodge(width=0.9), vjust=-0.25,size=12)+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(size = 50),
        axis.line = element_blank(),
        axis.text = element_text(size = 50),
        panel.border = element_rect(colour = "black", fill=NA, size=.8),
        panel.background = element_blank(),
        panel.grid.major.x= element_line(size = 1, linetype = "dashed",
                                         colour = "#c1c1c1"),
        # panel.grid.minor.x= element_line(size = 0.5, linetype = "dashed",
        # colour = "#c1c1c1"),
        
        panel.grid.major.y = element_line(size = 1, linetype = "dashed",
                                          colour = "#c1c1c1"),
        # panel.grid.minor.y = element_line(size = 0.5, linetype = "dashed",
        #                                   colour = "#c1c1c1"),
        panel.spacing = unit(0,"cm"),
        legend.title=element_blank(),
        legend.text = element_text(size = 50,color="#58585A"),
        legend.position = "bottom",
        legend.justification = .45,
        legend.key.width =  unit(1,"cm"),
        legend.spacing.x = unit(.5, "cm"),
        legend.spacing.y = unit(.9, "cm"),
        legend.key.size = unit(1, 'lines'),
        legend.key = element_rect(fill = NA),
        plot.margin = unit(c(.1, .1, 0, 0), "cm"),
        legend.text.align = 0,
        strip.text = element_text(size=50))+
    scale_y_continuous(labels = scales::percent)+
facet_wrap(~Camp,ncol = 6)+
  ylab("Perecent") +
  xlab("Level") 


```

## Number mean aggregated value by camp 
Mean aggregated value of total - **`r sum(dataset_2019_cleaned_for_charts$sum_value)/sum(dataset_2019_cleaned_for_charts$count_by_camp_level)`** 
```{r fig.height=50, fig.width=60}

dataset_2019_cleaned_for_charts_mean <- dataset_2019_cleaned_for_charts %>% dplyr::group_by(Camp) %>% dplyr::summarise(
  mean_value = round(mean(mean_by_camp),2)
)
ggplot(dataset_2019_cleaned_for_charts_mean) +
  geom_bar(aes(x = reorder(Camp, -mean_value),
               y= mean_value,
               color = Camp, 
               fill = Camp),
               position = "dodge",
               stat = "identity")+
  geom_text(aes(x=Camp,y=mean_value,label=mean_value), position=position_dodge(width=0.5), hjust=-.25,size=18)+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(size = 50),
        axis.line = element_blank(),
        axis.text = element_text(size = 50),
        panel.border = element_rect(colour = "black", fill=NA, size=.8),
        panel.background = element_blank(),
        panel.grid.major.x= element_line(size = 1, linetype = "dashed",
                                         colour = "#c1c1c1"),
        # panel.grid.minor.x= element_line(size = 0.5, linetype = "dashed",
        # colour = "#c1c1c1"),
        
        panel.grid.major.y = element_line(size = 1, linetype = "dashed",
                                          colour = "#c1c1c1"),
        # panel.grid.minor.y = element_line(size = 0.5, linetype = "dashed",
        #                                   colour = "#c1c1c1"),
        panel.spacing = unit(0,"cm"),
        legend.title=element_blank(),
        legend.text = element_blank(),
        legend.position = "none",
        legend.justification = .45,
        legend.key.width =  unit(1,"cm"),
        legend.spacing.x = unit(.5, "cm"),
        legend.spacing.y = unit(.9, "cm"),
        legend.key.size = unit(1, 'lines'),
        legend.key = element_rect(fill = NA),
        plot.margin = unit(c(.1, .1, 0, 0), "cm"),
        legend.text.align = 0,
        strip.text = element_text(size=50))+
  ylab("Camp") +
  xlab("Mean Value") +
  coord_flip()

```


## Change
Number of matched data - **`r nrow(matched_df_full)`** 
```{r}

 total_change %>% kable(longtable = T, booktabs = T, linesep = "",caption= "Total Number of change") %>% kable_styling(position = "center")


 percentage_change_by_implementing_partner %>% kable(longtable = T, booktabs = T, linesep = "",caption= "Change by implementing partner") %>% kable_styling(position = "center")
 
 change_between_level %>% kable(longtable = T, booktabs = T, linesep = "",caption= "change analysis by level") %>% kable_styling(position = "center")

 
all_df_for_under_6_age %>% kable(longtable = T, booktabs = T, linesep = "",caption= "number of promoted who are under age 6") %>% kable_styling(position = "center")
```